A cautionary note on the use of Ornstein Uhlenbeck and other models in macroevolutionary studies

### 2015-04-16 Manuscript/ohyou.tex
Minor edits
Edits to structure

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
\usepackage[round]{natbib} % author-year citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{enumerate} 
%\usepackage[nomarkers, nolists]{endfloat}  % To push floats to the end   
\pagenumbering{arabic}

@@

  One of the most commonly used Brownian-like models is the Ornstein Uhlenbeck (OU) model. 
  This is a modification of the Brownian model with an additional parameter $\alpha$ that measures the strength of return towards a theoretical optimum \citep{hansen1997stabilizing}. 
  The OU model was introduced to population genetics by \cite{Lande:1976aa} to model stabilizing selection in which the trait mean was recast as a fitness optimum on an adaptive landscape. 
  The process operating in comparative data is analogous, although clearly is not stabilizing selection, despite being sometimes referred to as such (see Discussion).

  The popularity of the OU model has grown extensively in recent years (Fig. \ref{figure.literature}); over 2500 ecology, evolution and palaeontology papers containing the phrase ``Ornstein Uhlenbeck'' were published between 2012 and 2014 (Google Scholar search 15th March 2015; see Supplementary Material). % Need to add ref to supp mat
  This may partly be because these models are now easy to implement apply via packages in R \citep[e.g. ouch, GEIGER and OUwie;][]{Butler:2004aa,Harmon:2008aa,beaulieu2012ouwie}. 
  Additionally, although the OU model is pattern-based, it has a number of attractive biological interpretations. 
  For example, fit to an OU model is used as evidence for processes such as phylogenetic niche conservatism, convergent evolution and stabilising selection \citep[e.g.,][]{Wiens:2010aa,christin2013anatomical,ingram2013surface}. 
  Unfortunately, although widely used, the properties of the OU model are poorly understood leading to the potential for inappropriate use and misinterpretation of results.

  The majority of papers use the OU model to model the evolution of a continuous character (Table \ref{table.uses}; Supplementary Material) therefore, we focus on this use of the OU model in our simulations below. 
  The principles here also apply to a range of other macroevolutionary models that can be fit to continuous data and compared using model testing procedures.
  Note that we focus on OU models with a single optimum trait value because these are more commonly used (Table \ref{table.uses}; Supplementary Material) and easier to simulate, but our general conclusions also apply to multiple optima OU models.

    \begin{table}[h]
        \caption{The most common uses of Ornstein Uhlenbeck models in ecology, evolutionary biology and palaeontology papers published between 2005 and 2013. See Supplementary Material for details.}
        \bigskip  
          \begin{tabular}{p{8cm}lc}
            \hline
            Use of OU model & Optima & Number of papers\\
            \hline
            Ancestral state reconstruction & single & 8\\
            & multiple & 2\\
            Convergent evolution & single & 0\\
            & multiple & 2\\
            Model of evolution & single & 31\\
            & multiple & 27\\
            Phylogenetic generalised least squares & single & 35\\
            & multiple & 0\\
            Other & single & 5\\
            & multiple & 5\\
            Total & single &  36\\
            & multiple & 79\\
            \hline
            \label{table.uses}
          \end{tabular}
    \end{table}

  Here we present simulations demonstrating the inherent bias in estimating the $\alpha$ parameter, discuss the intricacies of interpreting OU models biologically, and provide advice for appropriate use of OU models in phylogenetic comparative analyses. We also show that very small amounts of measurement error in data can have profound effects on the performance of models. 
  Many of our findings are applicable to other models of evolution (see Discussion and Supplemental Figs. S6-S11) 
  % Add figure refs here
  , but we focus on the OU model because of the recent increase in publications using the model and because of the under-appreciated ambiguity in the link between pattern and process when interpreting estimates of the $\alpha$ parameter. 
  We are not the first to mention these problems, but we hope by summarising the issues and giving recommendations we can help those less familiar with the technical literature \citep[e.g.,][]{ho2013asymptotic,ho2014intrinsic,boettiger2012your,hansen2012interpreting,ives2010phylogenetic}.

\section{Materials and Methods}
  \subsection{The Ornstein Uhlenbeck (OU) model}
    According to the Brownian model \citep{cavalli1967,felsenstein1973maximum}, a trait X evolves at random at a rate $\sigma$:

@@

    $\alpha$ can more easily be interpreted by using it to estimate the ``phylogenetic half-life'' ($t_\frac{1}{2}$) of a trait, i.e., the time it takes for a species entering a new niche to evolve halfway toward its new expected optimum \citep{hansen1997stabilizing}, as follows:

@@

  \subsection{Known statistical issues with the OU model}
  ???Problems with the OU model and where they are reported in the literature?

    \begin{enumerate}
      \item $\alpha$ is bounded at zero.
      \item blah
      \item measurement errors
    \end{enumerate}

  \subsection{Maximum Likelihood simulations}
  \label{section:sims.methods} 
    We used simulations to explore the statistical properties of $\alpha$. 
    We simulated phylogenies with 25, 50, 100, 150, 200, 500, or 1000 tips under pure birth, constant-rate Birth-Death (extinction fractions of 0.25, 0.5 and 0.75), or temporally varying speciation rate (speciation rate modeled as time from the root raised to the power 0.2, 0.5, 2 and 5) models. 
    We simulated 1000 phylogenies for each combination of tips and models resulting in 56,000 simulated phylogenies in total. 
    Trees were simulated using the R package TESS \cite{hohna2013fast}. 
    We then simulated the evolution of a single trait under a Brownian motion model on each phylogeny using the R package MOTMOT \citep{Thomas:2011aa}. 
    We estimated $\alpha$ and compared the fit of a Brownian model to that of an OU model using a likelihood ratio test with 1 degree of freedom with the \texttt{transformPhylo.ML} function in MOTMOT \citep{Thomas:2011aa}. 
    This procedure mirrors a situation where the OU model  %%% argh

  \subsection{Effects of measurement error}
    Measurement error can strongly effect the results of comparative analyses \cite{silvestro2015} so we also investigated whether adding error to our simulated data influenced estimates of $\alpha$.
    We used the same procedure as above to simulate trait data under a Brownian motion model with known error. 
    Specifically, we simulated trees under a Yule model with 25, 50, 100, 150, 200, 500, or 1000 tips and added branch length of (i) 1\%, (ii) 5\% or (iii) 10\% of the tree height to the tips of the simulated trees. 
    We then simulated data under a Brownian model on each tree. 
    We compared the fit of a Brownian model to that of an OU model using likelihood ratio tests as described above, using the original trees without the addition of extra branch length to the tip edges. 
    Our expectation is that the OU model should fit the data better than the Brownian model but the reason for the better fit would be entirely unrelated to any evolutionary process.

\section{Results}
  \subsection{Maximum Likelihood simulations}
  \label{section:sims.results}

    Figure \ref{figure.profiles} shows some examples of profile likelihoods for $\alpha$ generated on different datasets that were simulated according to a Brownian model. It is clear that the shape of the tree affects the shape of the likelihood profile. Trees with increasing speciation rates from root to tip (i.e., that have a lot of recently evolved species) generate very wide, flat likelihood profiles (Fig. \ref{figure.profiles}A). On the other hand, trees with declining speciation rates from root to tip (Fig. \ref{figure.profiles}B), or generated according to a Yule process (Fig. \ref{figure.profiles}C), yield more strongly peaked profiles.

%\begin{figure}
 % \centering
  %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure3.pdf}
  %\caption{Examples of profile likelihoods for selected simulated datasets. In all cases the ‘true’ value of alpha is 0.}
%\label{figure.profiles}
%\end{figure}

In all three cases, there are several features worth noting. First, the profiles are asymmetric. There is a hard bound at $\alpha = 0$, and as $\alpha$ becomes large, the rate of decrease in the likelihood slows. This is because, as shown in Figure \ref{figure.traitsim}, as values of $\alpha$ become large, the effects of changing $\alpha$ on model predictions are increasingly small. It is also notable, that the Maximum Likelihood estimates of $\alpha$ are, in most cases, between 0 and 1. In Figure \ref{figure.traitsim} it was noted that in this region of parameter space, the OU model is very difficult to distinguish from Brownian. This, combined with the asymmetric nature of the profile likelihood is suggestive that estimates of $\alpha$ are likely to be biased, and that the asymptotic assumptions of likelihood ratio tests on $\alpha$ are likely to be violated.

The effects of the asymmetric profile likelihoods become clear when calculating Type I error for the OU model based on ML estimates across a range of tree shapes and sizes (Fig. \ref{figure.rejection}; see Supplemental Figs. S2 and S3 for results with alternative priors for the Bayesian analyses). Regardless of tree shape, Type I error rates are unacceptably high when tree size is small (Figs. \ref{figure.rejection}A, \ref{figure.rejection}C and \ref{figure.rejection}E). For some tree shapes (particularly where speciation rates accelerate towards the present), Type I error remains $>0.05$ even for trees with 1000 tips. Bayesian estimation is not subject to bias % check in the log-likelihood statistic and consistently rejects the OU model. However, estimates of α are similar regardless of method.

%\begin{figure}
  %\centering
  %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure4.pdf}
  %\caption{Rejection rates and estimation of $\alpha$ for different tree sizes and shapes. Rejection rates (a,c,e) for the OU model at multiple tree sizes for models fitted using ML (circles) and Bayesian (diamonds) methods. Estimates of $\alpha$ (b,d,f) based on ML (circles show means and dotted lines show 95\% sampling interval from 1000 trees) and Bayesian (diamonds show means and dotted lines show 95\% sampling interval of the modal value from the posterior distribution from 1000 trees).}
%\label{figure.rejection}
%\end{figure}

%Figure \ref{figure.error} shows the proportion of data sets in which the OU model is favoured over the Brownian model for data simulated under Brownian motion with error (also see Figs. S4 and S5). The expectation is that the OU model should fit better because the branch length transformation partially captures the non-Brownian component (the error). There are two points worth noting. First, the frequency with which the OU model is favoured increases with tree size for both ML and Bayesian estimation (Fig. \ref{figure.error}A). With as little as 5\% error, the OU model becomes extremely difficult to reject, even for trees with just 100 species. This is important for the interpretation of the OU model. We cannot conclude anything about evolutionary process from a single optimum OU model unless error is adequately accounted for. Second, for moderate amounts of error (5-10\%), the ML estimates of $\alpha$ are consistently $>$ 1 (Fig. \ref{figure.error}B). Large values of $\alpha$ are similarly difficult to interpret because they are indicative that the signal of the past has been overwritten.

%\begin{figure}
 % \centering
  %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure5.pdf}
  %\caption{Rejection of BM with measurement error (a) and estimation of α (b). Symbols follow Figure \ref{figure.rejection}.}
%\label{figure.error}
%\end{figure}

The bias % check
 reported above are not unique to the OU model. The parameter $\delta$, which tests for accelerating or decelerating rates of evolution \citep{Pagel:1997aa,Pagel:1999aa} also suffers from elevated Type I error and is upwardly biased, favoring models that imply temporally increasing evolutionary rates (Supplemental Fig. S8). In contrast, although the speciational model ($\kappa$) has slightly elevated Type I errors, the parameter estimates are unbiased for the majority of tree sizes and shapes (Supplemental Fig. S6). As previously shown (Freckleton et al. 2002), the $\lambda$ model is conservative with low Type I error rates (Supplemental Fig. S7). As with the OU model, the $\delta$ models are all strongly favored over Brownian motion when there is error in the species data (Supplemental Figs. S9-S11).

\section{Discussion}
\label{section:discussion}

@@

%Results from \citet{ho2013asymptotic}, indicate that there is the potential for revealing strong biases in $\alpha$ , but the implications for practice (e.g. likelihood of rejection of alternative models) is unexplored other than to note that tree shape may play an influence.

%The modification of Brownian models to account for non-Brownian processes can be traced back to \citet{grafen1989phylogenetic} who introduced a parameter $\rho$ to account for non-linear scaling of evolutionary changes. $\rho$ is a power transformation of node heights in the phylogeny, and is fitted by maximum likelihood. It is worth noting that Grafen warned explicitly about potential drawbacks with $\rho$. Specifically: (i) the parameter is likely to be biased; (ii) its asymptotic sampling variance is non-zero; and (iii) values of the parameter should be interpreted cautiously. \citet{freckleton2002phylogenetic} showed that $\rho$ was indeed biased as predicted by Grafen (1989). They also showed that another parameter, Pagel’s $\lambda$ \citep{Pagel:1997aa,Pagel:1999aa}, also exhibited biases (but that these were likely to have minimal consequences in analyses using reasonable sample sizes). This strongly suggests that simulations are required to test the properties of such parameters, and that as recommended by \citet{grafen1989phylogenetic} “careless” parameterization of the phylogenetic variance-covariance matrix should be avoided.

>>>>

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
\usepackage[round]{natbib} % author-year citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{enumerate} 
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{fullpage}
\usepackage{hyperref}
%\usepackage[nomarkers, nolists]{endfloat}  % To push floats to the end   
\pagenumbering{arabic}

@@

  One of the most commonly used Brownian-like models is the Ornstein Uhlenbeck (OU) model. 
  This is a modification of the Brownian model with an additional parameter $\alpha$ that measures the strength of return towards a theoretical optimum \citep{hansen1997stabilizing}. 
  The model was introduced to population genetics by \cite{Lande:1976aa} to model stabilizing selection in which the trait mean was recast as a fitness optimum on an adaptive landscape. 
  The process operating in comparative data is analogous, although clearly is not stabilizing selection, despite being sometimes referred to as such (see section X).
  % Add section no here
  Unfortunately, although widely used, the properties of the OU model are poorly understood leading to the potential for inappropriate use and misinterpretation of results.

% This paragraph may need modifying once we finish
  In this paper we present an introduction to the OU model, its general properties and some issues with its use in ecology, evolution and palaeontology. 
  We use simulations to demonstrate the inherent bias in estimating the $\alpha$ parameter, discuss the intricacies of interpreting OU models biologically, and provide advice for appropriate use of OU models in phylogenetic comparative analyses. 
  We also show that very small amounts of measurement error in data can have profound effects on the performance of models. 
  Many of our findings are applicable to other models of evolution (see section X) 
  % Add section no here
  , but we focus on the OU model because of the recent increase in publications using the model and because of the under-appreciated ambiguity in the link between pattern and process when interpreting estimates of the $\alpha$ parameter. 
  We are not the first to mention these problems, but we hope by summarising the issues and giving recommendations we can help those less familiar with the technical literature \citep[e.g.,][]{ho2013asymptotic,ho2014intrinsic,boettiger2012your,hansen2012interpreting,ives2010phylogenetic}.

\section{The Ornstein Uhlenbeck (OU) model}

  According to the Brownian model \citep{cavalli1967,felsenstein1973maximum}, a trait X evolves at random at a rate $\sigma$:

@@

% Could move this down to the section on recommendations
    $\alpha$ can more easily be interpreted by using it to estimate the ``phylogenetic half-life'' ($t_\frac{1}{2}$) of a trait, i.e., the time it takes for a species entering a new niche to evolve halfway toward its new expected optimum \citep{hansen1997stabilizing}, as follows:

@@

  % I've left the actual details of the lit review in supp mat because I'm not usre how necessary they are here.
  \section{Uses of OU models}
  The popularity of the OU model has grown extensively in recent years (Fig. \ref{figure.literature}); over 2500 ecology, evolution and palaeontology papers containing the phrase ``Ornstein Uhlenbeck'' were published between 2012 and 2014 (Google Scholar search 15th March 2015; see Supplementary Material). % Need to add ref to supp mat
  This may partly be because these models are now easy to implement apply via packages in R \citep[e.g. ouch, GEIGER and OUwie;][]{Butler:2004aa,Harmon:2008aa,beaulieu2012ouwie}. 
  Additionally, although the OU model is pattern-based, it has a number of attractive biological interpretations. 
  For example, fit to an OU model is used as evidence for processes such as phylogenetic niche conservatism, convergent evolution and stabilising selection \citep[e.g.,][]{Wiens:2010aa,christin2013anatomical,ingram2013surface}.

  The majority of papers use the OU model to model the evolution of a continuous character (Table \ref{table.uses}; Supplementary Material) therefore, we focus on this use of the OU model in our simulations below. 
  The principles here also apply to a range of other macroevolutionary models that can be fit to continuous data and compared using model testing procedures (e.g., $\kappa$, $\lambda$, $\delta$, ACDC, Early Burst; \citealp{Pagel:1997aa,Pagel:1999aa,Blomberg:2003aa,Harmon:2008aa}).
  Note that we focus on OU models with a single optimum trait value because these are more commonly used (Table \ref{table.uses}; Supplementary Material) and easier to simulate, but our general conclusions also apply to multiple optima OU models.

    \begin{table}[h]
      \begin{center}
        \caption{The most common uses of Ornstein Uhlenbeck models in ecology, evolutionary biology and palaeontology papers published between 2005 and 2013. See Supplementary Material for details.}
        \bigskip  
          \begin{tabular}{p{8cm}lc}
            \hline
            Use of OU model & Optima & Number of papers\\
            \hline
            Ancestral state reconstruction & single & 8\\
            & multiple & 2\\
            Convergent evolution & single & 0\\
            & multiple & 2\\
            Model of evolution & single & 31\\
            & multiple & 27\\
            Phylogenetic generalised least squares & single & 35\\
            & multiple & 0\\
            Other & single & 5\\
            & multiple & 5\\
            Total & single &  79\\
            & multiple & 36\\
            \hline
            \label{table.uses}
          \end{tabular}
      \end{center}
    \end{table}

\section{Known statistical issues with the OU model}
% Problems with the OU model and where they are reported in the literature?
% Could rename this section also or move it. Whatever makes most sense.

    \begin{enumerate}
      \item $\alpha$ has a hard bound at zero, but no upper bound, meaning that the Maximum Likelihood profile is asymmetric. As values of $\alpha$ become larger, the effects of changing $\alpha$ on model predictions are increasingly small. This suggests that estimates of $\alpha$ are likely to be biased
      % make sure we really mean biased here
      , and that the asymptotic assumptions of Likelihood ratio tests on $\alpha$ are likely to be violated.
      \item blah
      \item measurement errors?
    \end{enumerate}

% I've separated this out a bit to try and make the progression more logical
% It's all a bit drafty at present so feel free to edit heavily - you've a better idea than me about the results anyway
\section{Performance of OU models using Maximum Likelihood simulations}
  To explore some issues with the OU model in more detail, we ran a number of simulations designed to mirror the use of OU models in the literature.

  \subsection{Simulating phylogenies and data}
    We simulated phylogenies with 25, 50, 100, 150, 200, 500, or 1000 tips under pure birth, constant-rate Birth-Death (extinction fractions of 0.25, 0.5 and 0.75), or temporally varying speciation rate (speciation rate modeled as time from the root raised to the power 0.2, 0.5, 2 and 5) models. 
    We simulated 1000 phylogenies for each combination of tips and models resulting in 56,000 simulated phylogenies in total. 
    Trees were simulated using the R package TESS \cite{hohna2013fast}. 
    We then simulated the evolution of a single trait under a Brownian motion model on each phylogeny using the R package MOTMOT \citep{Thomas:2011aa}. 
    All our simulated trees and data are available on GitHub: \href{https://github.com/nhcooper123/OhYou}{github.com/nhcooper123/OhYou}.

  \subsection{Performance of $\alpha$ and Likelihood ratio tests}
    To determine whether $\alpha$ is biased, and whether Likelihood ratio tests are appropriate for use with the OU model, we estimated $\alpha$ for each of our simulated phylogenies and data, and compared the fit of a Brownian model to that of an OU model using a Likelihood ratio test with 1 degree of freedom with the \texttt{transformPhylo.ML} function in MOTMOT \citep{Thomas:2011aa}. 
    This mirrors the common situation where researchers fit Brownian and OU models and then use Likelihood ratio tests to select the ``best'' model \citep{}. % Add citations
    We then estimated the rejection rate for each set of simulations, i.e., the proportion of times OU models are favoured relative to a Brownian motion model, even though the data were simulated under Brownian model. This gives us a measure of Type I error rate for the OU model.

% I ended up just LaTeXing this for our own amusement
      \begin{table}[!htbp]
        \begin{center}
        \caption{Rejection rate and $\alpha$ estimates for data simulated under a constant rate Brownian model on a range of constant-rate birth death trees. Tree type refers to the extinction fraction for the birth-death trees. The rejection rate is the proportion of OU models favoured relative to a Brownian motion model.}
        \bigskip
        \input{Tables/OU_bd_noerror.tex}
        \label{tables:bd_noerror}
        \end{center}
      \end{table}

    We find that Type I error rates are unacceptably high when tree size is small (Table \ref{tables:bd_noerror}). 
    %For some tree shapes (particularly where speciation rates accelerate towards the present), Type I error remains $>0.05$ even for trees with 1000 tips.
    % I think we're cutting this?
    This has clear implications for studies with low sample sizes where OU is favoured.

% Could put in something about interpreting parameters here?

\section{Effects of measurement error on OU model performance}
  Measurement error can strongly effect the results of comparative analyses \cite{silvestro2015}, and appears to influence whether OU is the favoured model across a range of datasets \citep{} % add citation to Matt's model adequacy stuff
  Therefore, we also investigated whether adding error to our simulated data influenced estimates of $\alpha$.

  \subsection{Simulating phylogenies and data with error}
    We used the same procedure as above to simulate trait data under a Brownian motion model with known error. 
    % should we say "as above" here or be specific i.e. copy paste from above?
    Specifically, we simulated trees under a Yule model with 25, 50, 100, 150, 200, 500, or 1000 tips and added branch length of (i) 1\%, (ii) 5\% or (iii) 10\% of the tree height to the tips of the simulated trees. 
    We then simulated data under a Brownian model on each tree. 
    All our simulated trees and data are available on GitHub: \href{https://github.com/nhcooper123/OhYou}{github.com/nhcooper123/OhYou}.

  \subsection{Effects of measurement error on OU model performance}
    We compared the fit of a Brownian model to that of an OU model using likelihood ratio tests as described above, using the original trees without the addition of extra branch length to the tip edges. 
    Our expectation is that the OU model should fit the data better than the Brownian model but the reason for the better fit would be entirely unrelated to any evolutionary process.

% OK this is still broken!!!
  \begin{landscape}
      \begin{table}[!htbp]
        \begin{center}
        \caption{Rejection rate and $\alpha$ estimates for data simulated under a constant rate Brownian model with 0, 1, 5, or 10\% measurement error (m.e.). The rejection rate is the proportion of OU models favoured relative to a Brownian motion model.}
        \bigskip
        \input{Tables/OU_yule_error.tex}
        \label{tables:yule_error}
        \end{center}
      \end{table}
  \end{landscape}

    Table \ref{tables:yule_error} shows the proportion of data sets in which the OU model is favoured over the Brownian model for data simulated under Brownian motion with error. The expectation is that the OU model should fit better because the branch length transformation partially captures the non-Brownian component (the error). There are two points worth noting. First, the frequency with which the OU model is favoured increases with tree size for both ML and Bayesian estimation (Fig. \ref{tables:yule_error}). With as little as 5\% error, the OU model becomes extremely difficult to reject, even for trees with just 100 species. This is important for the interpretation of the OU model. We cannot conclude anything about evolutionary process from a single optimum OU model unless error is adequately accounted for. Second, for moderate amounts of error (5-10\%), the ML estimates of $\alpha$ are consistently $>$ 1. Large values of $\alpha$ are similarly difficult to interpret because they are indicative that the signal of the past has been overwritten.

\section{Prospects/ recommendations}
  \subsection{Brief discussion on methods and limitations for including measurement error}

@@

\section{Bayesian methods (available in BayesTraits, diversitree, others?; simulations back in; improves error rates but difficult challenge of choosing the right priors)}

\section{Just an OU problem? - Other parameters have similar problems (reduced set of our simulations for kappa, delta, lambda, e.g. just with Yule trees an error)}

 % The bias % check we mean bias
 % reported above are not unique to the OU model. The parameter $\delta$, which tests for accelerating or decelerating rates of evolution \citep{Pagel:1997aa,Pagel:1999aa} also suffers from elevated Type I error and is upwardly biased, favoring models that imply temporally increasing evolutionary rates (Supplemental Fig. S8). In contrast, although the speciational model ($\kappa$) has slightly elevated Type I errors, the parameter estimates are unbiased for the majority of tree sizes and shapes (Supplemental Fig. S6). As previously shown (Freckleton et al. 2002), the $\lambda$ model is conservative with low Type I error rates (Supplemental Fig. S7). As with the OU model, the $\delta$ models are all strongly favored over Brownian motion when there is error in the species data (Supplemental Figs. S9-S11).

\section{Concluding comments/Conclusions}
\section{Epilogue - vaguely reproducible science}

%--------------------------------------
% I've left all this as is for now as we can slot relevant paragraphs into the appropriate places

\section{Discussion}

% This came from the intro but fits better later
%The modification of Brownian models to account for non-Brownian processes can be traced back to \citet{grafen1989phylogenetic} who introduced a parameter $\rho$ to account for non-linear scaling of evolutionary changes. $\rho$ is a power transformation of node heights in the phylogeny, and is fitted by maximum likelihood. It is worth noting that Grafen warned explicitly about potential drawbacks with $\rho$. Specifically: (i) the parameter is likely to be biased; (ii) its asymptotic sampling variance is non-zero; and (iii) values of the parameter should be interpreted cautiously. \citet{freckleton2002phylogenetic} showed that $\rho$ was indeed biased as predicted by Grafen (1989). They also showed that another parameter, Pagel’s $\lambda$ \citep{Pagel:1997aa,Pagel:1999aa}, also exhibited biases (but that these were likely to have minimal consequences in analyses using reasonable sample sizes). This strongly suggests that simulations are required to test the properties of such parameters, and that as recommended by \citet{grafen1989phylogenetic} “careless” parameterization of the phylogenetic variance-covariance matrix should be avoided.
